Desigualdad económica y su influencia sobre la percepción de las diferencias de ingreso legítimas

### 2019-12-11 index.rmd
update1012

---
author:
- Julio Iturra Sanhueza
- Catalina Rufs
- Juan Carlos Castillo
bibliography:
- 'bib/zlibrary.bib'
csl:
- 'bib/apa6.csl'
title: Desigualdad económica y su influencia sobre la percepción de las
        diferencias de ingreso legítimas
output:
    word_document:
       reference_docx: "bib/my-styles.docx"
    html_document:
      theme: cosmo
      number_sections: true
css: "bib/style.css"
---

>>>>

---
author:
- Julio Iturra Sanhueza
- Catalina Rufs
- Juan Carlos Castillo
bibliography:
- 'bib/zlibrary.bib'
csl:
- 'bib/apa6.csl'
title: "Desigualdad económica y su influencia sobre la percepción de las diferencias de ingreso legítimas"
output:
    word_document:
       reference_docx: "bib/my-styles.docx"
    html_document:
      theme: cosmo
      number_sections: true
css: "bib/style.css"
---
